Continuous developmental change can explain discontinuities in word learning

### 2019-07-22 journal/ms.Rmd
journal vers

We use a case study from word learning literature. @stager1997 first showed that children's early ability to distinguish similar sounds does not automatically translate into word learning skills. The authors measured word learning using an audio-visual habituation Switch task. First, infants are familiarized with two word-object pairings (e.g., Word A with Object A and Word B with Object B). Second, they are tested using two types of trials. The control 'same' trial consists of a correct pairing  (e.g., Word A with Object A) and the 'switch' trial consists of a wrong pairing (e.g., Word A with Object B). If babies have correctly learned the association during the familiarization, they are supposed to be surprised by the 'switch' trial and not by the 'same' trial. The former should thus result in a greater looking time compared to the latter [@werker1998].

Though infants around 14-month old can distinguish perceptually similar sound pairs such as "dih" and "bih", they appear to fail in mapping this pair to two different objects in the switch task. This failure has initially been taken as evidence that 14-month olds do not encode subtle sounds during meaning learning [@stager1997; @pater2004]. This interpretation suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children, around 17 months [@werker2002], typically do.

@@

Our finding that word learning is mediated by the visual similaérity of the semantic objects has implications for theories of lexical development. It suggests that, all things being equal, children may prioritize the acquisition of words whose semantic referents are visually different, as this allows them to minimize semantic ambiguity. It will be interesting for future work to explore whether the results that we obtained using visual similarity generalize to richer, more conceptual features in the semantic space. This suggestion is, indeed, supported by recent work investigating vocabulary development [@engelthaler2017; @sizemore2018; @fourtassi2018]

>>>>

We use a case study from word learning literature. @stager1997 first showed that children's early ability to distinguish similar sounds does not automatically translate into word learning skills. The authors measured word learning using an audio-visual habituation Switch task. First, infants are familiarized with two word-object pairings (e.g., lable A with object A and label B with object B). Second, they are tested using two types of trials. The control 'same' trial consists of a correct pairing  (e.g., label A with object A) and the 'switch' trial consists of a wrong pairing (e.g., label A with object B). If babies have correctly learned the association during the familiarization, they are supposed to be surprised by the 'switch' trial and not by the 'same' trial. The former should thus result in a greater looking time compared to the latter [@werker1998].

Though infants around 14-month old can distinguish perceptually similar sound pairs such as "dih" and "bih", they appear to fail in mapping this pair to two different objects in the switch task. This failure has initially been taken as evidence that 14-month olds do not encode subtle sounds during meaning learning [@stager1997; @pater2004]. This interpretation suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children, around 17 months, typically do [@werker2002].

@@

Our finding that word learning is mediated by the visual similarity of the semantic objects has implications for theories of lexical development. It suggests that, all things being equal, children may prioritize the acquisition of words whose semantic referents are visually different, as this allows them to minimize semantic ambiguity. It will be interesting for future work to explore whether the results that we obtained using visual similarity generalize to richer, more conceptual features in the semantic space. This suggestion is, indeed, supported by recent work investigating vocabulary development [@engelthaler2017; @sizemore2018; @fourtassi2018]

### 2019-07-22 journal/ms.tex
journal vers

We use a case study from word learning literature. Stager and Werker
(1997) first showed that children's early ability to distinguish similar
sounds does not automatically translate into word learning skills. The
authors measured word learning using an audio-visual habituation Switch
task. First, infants are familiarized with two word-object pairings
(e.g., Word A with Object A and Word B with Object B). Second, they are
tested using two types of trials. The control \enquote{same} trial
consists of a correct pairing (e.g., Word A with Object A) and the
\enquote{switch} trial consists of a wrong pairing (e.g., Word A with
Object B). If babies have correctly learned the association during the
familiarization, they are supposed to be surprised by the
\enquote{switch} trial and not by the \enquote{same} trial. The former
should thus result in a greater looking time compared to the latter
(Werker, Cohen, Lloyd, Casasola, \& Stager, 1998).

Though infants around 14-month old can distinguish perceptually similar
sound pairs such as \enquote{dih} and \enquote{bih}, they appear to fail
in mapping this pair to two different objects in the switch task. This
failure has initially been taken as evidence that 14-month olds do not
encode subtle sounds during meaning learning (Pater, Stager, \& Werker,
2004; Stager \& Werker, 1997). This interpretation suggested a
discontinuous/stage-like pattern of development whereby younger children
fail to encode the contrastive phonetic detail, whereas older children,
around 17 months (Werker, Fennell, Corcoran, \& Stager, 2002), typically
do.

@@

Our finding that word learning is mediated by the visual similaérity of
the semantic objects has implications for theories of lexical
development. It suggests that, all things being equal, children may
prioritize the acquisition of words whose semantic referents are
visually different, as this allows them to minimize semantic ambiguity.
It will be interesting for future work to explore whether the results
that we obtained using visual similarity generalize to richer, more
conceptual features in the semantic space. This suggestion is, indeed,
supported by recent work investigating vocabulary development
(Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018; Sizemore,
Karuza, Giusti, \& Bassett, 2018)

>>>>

We use a case study from word learning literature. Stager and Werker
(1997) first showed that children's early ability to distinguish similar
sounds does not automatically translate into word learning skills. The
authors measured word learning using an audio-visual habituation Switch
task. First, infants are familiarized with two word-object pairings
(e.g., lable A with object A and label B with object B). Second, they
are tested using two types of trials. The control \enquote{same} trial
consists of a correct pairing (e.g., label A with object A) and the
\enquote{switch} trial consists of a wrong pairing (e.g., label A with
object B). If babies have correctly learned the association during the
familiarization, they are supposed to be surprised by the
\enquote{switch} trial and not by the \enquote{same} trial. The former
should thus result in a greater looking time compared to the latter
(Werker, Cohen, Lloyd, Casasola, \& Stager, 1998).

Though infants around 14-month old can distinguish perceptually similar
sound pairs such as \enquote{dih} and \enquote{bih}, they appear to fail
in mapping this pair to two different objects in the switch task. This
failure has initially been taken as evidence that 14-month olds do not
encode subtle sounds during meaning learning (Pater, Stager, \& Werker,
2004; Stager \& Werker, 1997). This interpretation suggested a
discontinuous/stage-like pattern of development whereby younger children
fail to encode the contrastive phonetic detail, whereas older children,
around 17 months, typically do (Werker, Fennell, Corcoran, \& Stager,
2002).

@@

Our finding that word learning is mediated by the visual similarity of
the semantic objects has implications for theories of lexical
development. It suggests that, all things being equal, children may
prioritize the acquisition of words whose semantic referents are
visually different, as this allows them to minimize semantic ambiguity.
It will be interesting for future work to explore whether the results
that we obtained using visual similarity generalize to richer, more
conceptual features in the semantic space. This suggestion is, indeed,
supported by recent work investigating vocabulary development
(Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018; Sizemore,
Karuza, Giusti, \& Bassett, 2018)
